\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{SmarteRun: Coding The Portable Coach}

### 2014-05-12 final/article.tex
Fix crazy figure 4 float

However, we have two implicit truths about these predictions. The first is that predicting pace for shorter runs should be easier (more accurate) than doing so for longer runs. This is because pace can vary less over a shorter run, so we would assume less possible variance in our model. The second is that predicting pace in the second half of a run should be more accurate than doing so for the first half of the run. This is because the second half of the run is by default closer to the end, so runners? parameters have less time to change. We decided to test these two assumptions, with the specific goal of making sure that we still have reasonable accuracy over the harder of these two problems. This is also a useful benchmark, as future optimizations should not just attempt to reduce RMSE, but also attempt to increase accuracy for these harder subsets of the problem.\\

@@

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{halves.png}
\caption{A graph comparing actual pace with predicted pace with predictions made in the first half of a run shown in blue and those in the second half of a run in red. }
\end{center}
\end{figure}

>>>>

However, we have two implicit truths about these predictions. The first is that predicting pace for shorter runs should be easier (more accurate) than doing so for longer runs. This is because pace can vary less over a shorter run, so we would assume less possible variance in our model. The second is that predicting pace in the second half of a run should be more accurate than doing so for the first half of the run. This is because the second half of the run is by default closer to the end, so runners' parameters have less time to change. \\

We decided to test these two assumptions, with the specific goal of making sure that we still have reasonable accuracy over the harder of these two problems. This is also a useful benchmark, as future optimizations should not just attempt to reduce RMSE, but also attempt to increase accuracy for these harder subsets of the problem.\\

@@

 \begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{halves.png}
\caption{A graph comparing actual pace with predicted pace. Predictions made in the first half of a run are shown in blue and those in the second half of a run in red. }
\end{center}
\end{figure}

@@
